---
title: "A UN Report on the Relationship between GDP and CO2 Emissions"
author: "Ben K"
date: "2023-01-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-packages}
library(tidyverse)
library(rstatix)
```
This report was prepared to the attention of the United Nations. It analyzes the relationship between a country's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country’s economic strength or weakness may be related to its public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions increase with a country's GDP.

``` {r read-data}
gapminder_1997 <- read_csv("data/gapminder_1997.csv")
```
```{r gdp-lifeExp-1997-plot, echo = FALSE, width = 6, height = 4, dpi = 300}
# make plot of GDP (x-axis) vs lifeExp (y-axis)
ggplot(gapminder_1997)+
  aes(x = gdpPercap, y = lifeExp, color = continent)+
  labs(x = "GDP Per Capita", y = "Life Expectancy (Years)", title = "Relationship between Life Expectancy and GDP")+
  geom_point()+
    theme_classic()+
    scale_color_brewer(palette = "Set1")
```

